Estimating nucleon substructure properties in a\\[.2ex] unified model of p-Pb and Pb-Pb collisions

### 2018-05-11 talk/qm2018.tex
Working version before departure

\newcommand{\trento}{T\raisebox{-0.3ex}{R}ENTo}
\newcommand{\T}{\tilde{T}}
\newcommand{\sqrts}{\sqrt{s_{NN}}}
\newcommand{\sigmaf}{\sigma_\text{fluct}}
\newcommand{\X}{\chi_\text{struct}}
\newcommand{\npartons}{n_\text{partons}}
\newcommand{\dmin}{d_\text{min}^3}
\newcommand{\conference}{\scshape Quark Matter \enskip\textbar\enskip Venice, Italy}
\newcommand{\paddedhline}{\noalign{\smallskip}\hline\noalign{\smallskip}}
\newcommand{\boundellipse}[3]% center, x rad, y rad
{(#1) ellipse [x radius=#2, y radius=#3]
}

@@

\begin{frame}{\scshape Collectivity in small systems, is it flow?}
  \smallskip
  \begin{columns}[T]
    \begin{column}{.62\textwidth}
      \bigskip
      Important questions:\\
      \begin{itemize}
        \item Is hydro applicable to small collision systems?
        \item If so, can small system collectivity be described using current hydro models?
      \end{itemize}
      \smallskip
      First question precludes the second, but also more difficult to answer.\\[1ex]
      Let's tackle the second question \textit{assuming} hydrodynamic models make
      sense down to length scales $\Delta x=.2$~fm.\\[1ex]
      Under this assumption, does a unified hydrodynamic description of p+A and A+A data exist?
    \end{column}
    \begin{column}{.3\textwidth}
      \centering
      \includegraphics[width=\columnwidth]{pbpb_corr2d}\\
      \includegraphics[width=\columnwidth]{ppb_corr2d}
    \end{column}
  \end{columns}

@@

\begin{frame}{Challenge of rigorous model-to-data comparison}
  \begin{figure}
    \begin{tikzpicture}
        \node [anchor=east, left=1cm  of current page.center, yshift=1.5cm]
          (t1) {\large \color{theme} Parameters};
        \node [anchor=east, left=1cm  of current page.center, yshift=1cm]
            (a1) {\small shear viscosity};
        \node [anchor=east, left=1cm  of current page.center, yshift=.5cm]
            (a2) {\small bulk viscosity};
        \node [anchor=east, left=1cm  of current page.center, yshift=0cm]
            (a3) {\small pre-equilibrium flow};
        \node [anchor=east, left=1cm  of current page.center, yshift=-.5cm]
            (a4) {\small nucleon size};
        \node [anchor=east, left=1cm  of current page.center, yshift=-1cm]
            (a5) {\small nucleon shape};

@@

\begin{frame}[t, plain]{\scshape Nucleon substructure}
  \vspace{2em}
  \begin{columns}[t]
    \begin{column}{.2\textwidth}
      \centering \small Sampling radius
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw[thick] (0,0) circle [radius= 1cm] node (A) {\normalsize 1 fm};
          \draw[thick] (0,-2) circle [radius=.8cm] node (B) {\small .8 fm};
          \draw[thick] (0,-3.6) circle [radius=.6cm] node (C) {\scriptsize .6 fm};
          \draw [thick] (0,-4.8) circle [radius=.4cm] node (D) {\tiny .4 fm};
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.2\textwidth}
      \centering \small Constituent width
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0, 0) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.3) circle (.6cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-2.2cm] circle (.4cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.2cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.23\textwidth}
      \centering \small Constituent number
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0,0) circle (1cm);
          \foreach \theta/\radius in {
            36/0.48, 72/0.6, 108/0.6, 140/0.36, 172/0.12,
            190/0.6, 240/0.36, 272/0.6, 308/0.48, 360/0.6
          }{
            \draw [thick] ({\theta}:\radius) circle (.3cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta/\radius in {
            0/.4, 65/.5, 115/.45, 190/.53, 240/.44, 310/.62
          }{
            \draw [thick] ({\theta}:\radius) [yshift=-2.2cm] circle (.3cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.3cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.37\textwidth}
      \centering
      \textcolor{theme}{Free parameters:}\\[1ex]
      \begin{itemize}
        \small
        \item Radius of Gaussian distribution used to sample
          constituent positions
        \item Gaussian constituent width
        \item Number of constituents in each nucleon
      \end{itemize}
      \bigskip
      \textcolor{theme}{Absent from this work:}\\[1ex]
      \begin{itemize}
        \small
        \item Spatial correlations,
          see talk by Alba Soto Ontoso
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Computer experiment design}
  \bigskip
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      \scriptsize
      \begin{tabular}{lll}
        Parameter         & Description                        & Range           \\
        \paddedhline
        Norm              & Overall normalization              & 12--28          \\
        $p$               & Entropy deposition parameter       & $-1$ to $+1$    \\
        $\sigmaf$         & Relative parton fluct. std.\       & 0--2            \\
        $r$               & Parton sampling radius             & 0.4--1.2 fm     \\
        $\X$              & Parton structure parameter         & 0--1            \\
        $m$               & Number of constituents             & 1--10           \\
        $\dmin$           & Nucleon exclusion volume           & 0--4.9 fm$^3$   \\
        $\tau_{fs}$       & Free streaming time                & 0.1--1.5 fm/$c$ \\
        $\eta/s$ min      & Shear viscosity at $T_c$           & 0--0.2          \\
        $\eta/s$ slope    & Slope above $T_c$                  & 0--8 GeV$^{-1}$ \\
        $\eta/s$ crv      & Curvature above $T_c$              & $-1$ to $1$     \\
        $\zeta/s$ norm    & Bulk viscosity peak height         & 0--0.1          \\
        $\zeta/s$ width   & Bulk viscosity peak width          & 0--0.1 GeV      \\
        $\zeta/s$ temp    & Bulk viscosity peak location       & 150--200 MeV    \\
        $T_\text{switch}$ & Particlization temperature         & 135--165 MeV    \\
      \end{tabular}
    \end{column}
    \begin{column}{.4\textwidth}
      \textcolor{theme}{\scshape Important details:}
      \smallskip
      \begin{itemize}
        \small
        \item Recast constituent width $w$ as:\\[1ex]
          $w = w_\text{min} + \X(w_\text{max} - w_\text{min})$\\[1ex]
          $w_\text{min} = 0.2$~fm,~ $w_\text{max} = r$\\[1ex]
        \item Parton sampling radius is \emph{not} equivalent to the proton radius
          in the proton c.o.m.\ frame, see\\
          \textcolor{theme}{\scriptsize PRC.94.024919}\\[1ex]
        \item Other parameters same as combined Pb+Pb analysis at 2.76 and 5.02 TeV
      \end{itemize}
    \end{column}
  \end{columns}
  \begin{center}
    \color{theme}
    500 design points per collision system, $\mathcal{O}(10^4)$ events per design point!
  \end{center}
\end{frame}

>>>>

\newcommand{\trento}{T\raisebox{-0.3ex}{R}ENTo}
\newcommand{\T}{\tilde{T}}
\newcommand{\sqrts}{\sqrt{s_{NN}}}
\newcommand{\sigmaf}{\sigma_\text{fluct}}
\newcommand{\X}{\chi_\text{struct}}
\newcommand{\dmin}{d_\text{min}^3}
\newcommand{\conference}{\scshape Quark Matter \enskip\textbar\enskip Venice, Italy}
\newcommand{\paddedhline}{\noalign{\smallskip}\hline\noalign{\smallskip}}
\newcommand{\boundellipse}[3]% center, x rad, y rad
{(#1) ellipse [x radius=#2, y radius=#3]
}

@@

\begin{frame}{\scshape Collectivity in small systems, is it flow?}
  \smallskip
  \begin{columns}[T]
    \begin{column}{.7\textwidth}
      \medskip \small
      \textcolor{theme}{\scshape Narrative:}\\[.5ex]
      Multiparticle correlations in A-A collisions are explained by flow.\\[1ex]
      \textcolor{theme}{\scshape Justification:}\\[.5ex]
      Quantitative agreement of hydrodynamic simulations remains strongest evidence for flow in A-A collisions. Agreement is global, self-consistent and highly non-trivial.\\[1ex]
      \textcolor{theme}{\scshape Natural questions:}\\[.5ex]
      Can the same framework simultaneously describe p-A collisions without spoiling its description of A-A collisions? Does the framework continue to make sense?\\[1ex]
      \textcolor{theme}{\scshape This work:}\\[.5ex]
      Calibrate a successful hybrid model---based on viscous hydrodynamics and Boltzmann transport---to simultaneously describe p-Pb and Pb-Pb data. Does such a description exist?
    \end{column}
    \begin{column}{.3\textwidth}
      \centering
      \includegraphics[width=\columnwidth]{pbpb_corr2d}\\
      \includegraphics[width=\columnwidth]{ppb_corr2d}
    \end{column}
  \end{columns}

@@

\begin{frame}{\scshape Challenge of rigorous model-to-data comparison}
  \begin{figure}
    \begin{tikzpicture}
        \node [anchor=east, left=1cm  of current page.center, yshift=1.5cm]
          (t1) {\large \color{theme} Parameters};
        \node [anchor=east, left=1cm  of current page.center, yshift=1cm]
            (a1) {\small shear viscosity};
        \node [anchor=east, left=1cm  of current page.center, yshift=.5cm]
            (a2) {\small bulk viscosity};
        \node [anchor=east, left=1cm  of current page.center, yshift=0cm]
            (a3) {\small pre-equilibrium flow};
        \node [anchor=east, left=1cm  of current page.center, yshift=-.5cm]
            (a4) {\small nucleon size};
        \node [anchor=east, left=1cm  of current page.center, yshift=-1cm]
            (a5) {\small nucleon shape};
        \node [anchor=east, left=1cm  of current page.center, yshift=-1.5cm]
            (a6) {\small and more...};

@@

\begin{frame}[t, plain]{\scshape Nucleon substructure}
  \vspace{2em}
  \begin{columns}[t]
    \begin{column}{.2\textwidth}
      \centering \small Sampling radius
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw[thick] (0,0) circle [radius= 1cm] node (A) {\normalsize 1 fm};
          \draw[thick] (0,-2) circle [radius=.8cm] node (B) {\small .8 fm};
          \draw[thick] (0,-3.6) circle [radius=.6cm] node (C) {\scriptsize .6 fm};
          \draw [thick] (0,-4.8) circle [radius=.4cm] node (D) {\tiny .4 fm};
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.2\textwidth}
      \centering \small Constituent width
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0, 0) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.3) circle (.6cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-2.2cm] circle (.4cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.2cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.23\textwidth}
      \centering \small Constituent number
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0,0) circle (1cm);
          \foreach \theta/\radius in {
            36/0.48, 72/0.6, 108/0.6, 140/0.36, 172/0.12,
            190/0.6, 240/0.36, 272/0.6, 308/0.48, 360/0.6
          }{
            \draw [thick] ({\theta}:\radius) circle (.3cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta/\radius in {
            0/.4, 65/.5, 115/.45, 190/.53, 240/.44, 310/.62
          }{
            \draw [thick] ({\theta}:\radius) [yshift=-2.2cm] circle (.3cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.3cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.37\textwidth}
      \centering
      \textcolor{theme}{Free parameters:}\\[1ex]
      \begin{itemize}
        \small
        \item Sampling radius of constituent positions
        \item Constituent Gaussian width
        \item Number of constituents in each nucleon
      \end{itemize}
      \bigskip
      \textcolor{theme}{Absent from this work:}\\[1ex]
      \begin{itemize}
        \small
        \item Spatial correlations,
          see talk by Alba Soto Ontoso
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Computer experiment design}
  \bigskip
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      \scriptsize
      \begin{tabular}{lll}
        Parameter         & Description                        & Range           \\
        \paddedhline
        Norm              & Overall normalization              & 12--28          \\
        $p$               & Entropy deposition parameter       & $-1$ to $+1$    \\
        $\sigmaf$         & Relative constituent fluct. std.\  & 0--2            \\
        $r$               & Constituent sampling radius        & 0.4--1.2 fm     \\
        $\X$              & Constituent structure parameter    & 0--1            \\
        $m$               & Number of constituents             & 1--9            \\
        $\dmin$           & Nucleon exclusion volume           & 0--4.9 fm$^3$   \\
        $\tau_{fs}$       & Free streaming time                & 0.1--1.5 fm/$c$ \\
        $\eta/s$ min      & Shear viscosity at $T_c$           & 0--0.2          \\
        $\eta/s$ slope    & Slope above $T_c$                  & 0--8 GeV$^{-1}$ \\
        $\eta/s$ crv      & Curvature above $T_c$              & $-1$ to $1$     \\
        $\zeta/s$ norm    & Bulk viscosity peak height         & 0--0.1          \\
        $\zeta/s$ width   & Bulk viscosity peak width          & 0--0.1 GeV      \\
        $\zeta/s$ temp    & Bulk viscosity peak location       & 150--200 MeV    \\
        $T_\text{switch}$ & Particlization temperature         & 135--165 MeV    \\
      \end{tabular}
    \end{column}
    \begin{column}{.4\textwidth}
      \textcolor{theme}{\scshape Important details:}
      \smallskip
      \begin{itemize}
        \small
        \item Recast constituent width $w$ as:\\[1ex]
          $w = w_\text{min} + \X(w_\text{max} - w_\text{min})$\\[1ex]
          $w_\text{min} = 0.2$~fm,~ $w_\text{max} = r$\\[1ex]
        \item Constituent sampling radius is \emph{not} equivalent to the proton radius
          in the proton c.o.m.\ frame, see~ \textcolor{theme}{\scriptsize PRC.94.024919}\\[1ex]
        \item Other parameters same as combined Pb+Pb analysis at 2.76 and 5.02 TeV
      \end{itemize}
    \end{column}
  \end{columns}
  \begin{center}
    \color{theme}
    500 design points per collision system, $\mathcal{O}(10^4)$ events per design point!
  \end{center}
\end{frame}
